
    \documentclass[letterpaper,11pt]{article}
    \newlength{\outerbordwidth}
    \pagestyle{empty}
    \raggedbottom
    \raggedright
    \usepackage[svgnames]{xcolor}
    \usepackage{framed}
    \usepackage{tocloft}

    \usepackage[T1]{fontenc}
    \usepackage{lmodern}
    \usepackage[utf8]{inputenc}
    \usepackage[]{babel}
    \usepackage{fontawesome}
    \usepackage{hyperref}

    %-----------------------------------------------------------
    %Edit these values as you see fit

    \setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars
    \definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
    \definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

    %-----------------------------------------------------------
    %Margin setup

    \setlength{\evensidemargin}{-0.25in}
    \setlength{\headheight}{0in}
    \setlength{\headsep}{0in}
    \setlength{\oddsidemargin}{-0.25in}
    \setlength{\paperheight}{11in}
    \setlength{\paperwidth}{8.5in}
    \setlength{\tabcolsep}{0in}
    \setlength{\textheight}{9.5in}
    \setlength{\textwidth}{7in}
    \setlength{\topmargin}{-0.3in}
    \setlength{\topskip}{0in}
    \setlength{\voffset}{0.1in}

    %-----------------------------------------------------------
    %Custom commands
    \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
    \newcommand{\resheading}[1]{\vspace{6pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
    \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.8in][l]{\large #1} \vphantom{p\^{E}}}}}}
        \end{shaded}
    }\vspace{-6pt}
    }
    \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{p{4.8in}@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-8pt}}
    %-----------------------------------------------------------

    \begin{document}
    
      \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large Andrew Qiao} & 647-621-0369 \\
      Waterloo, Canada & andrew.qiao@uwaterloo.ca \\
      \faGithub { }  \href{https://github.com/andrewqiao}{https://github.com/andrewqiao} & \\
      \faLinkedin { }  \href{https://linkedin.com/in/andrewqiao}{https://linkedin.com/in/andrewqiao} & \\
      \end{tabular*}
      \vspace{5pt}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Summary}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
      \item[] Highly accomplished Computer Science student at the University of Waterloo with extensive experience in developing production-grade AI applications and scalable software systems. Proven track record in leveraging frontier AI technologies, including Retrieval-Augmented Generation (RAG), Large Language Models (LLMs), and vector databases to solve complex enterprise problems. Demonstrated expertise in building AI copilots, generative AI applications, and high-performance distributed systems at industry leaders like Snowflake and IBM. Adept at bridging the gap between cutting-edge research and impactful engineering, with a strong foundation in software architecture, CI/CD, and cloud-native development.
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Work Experience}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Ramp}{Waterloo, Canada}{Incoming Software Engineer Intern}{Sept. 2025 - Dec. 2025}
        \begin{itemize}
            \resitem{Selected for upcoming software engineering internship to contribute to high-scale financial technology solutions.}
        \end{itemize}
        \item \ressubheading{Snowflake}{Waterloo, Canada}{Software Engineer Intern}{Apr. 2025 - Now}
        \begin{itemize}
            \resitem{Developing Snowflake's design system consumed by 100+ engineers using React.js, TypeScript, and StyleX.}
            \resitem{Accelerating the development of polished, accessible, and consistent user experiences across the platform.}
        \end{itemize}
        \item \ressubheading{Snowflake}{Waterloo, Canada}{Software Engineer (Contract)}{Not Specified - Not Specified}
        \begin{itemize}
            \resitem{Built AI Copilot for Notebooks, accelerating workflows for 1,000+ data scientists across 300+ organizations.}
            \resitem{Owned development of resource monitoring in Notebooks using Python, gRPC, Protocol Buffers, React.js, TypeScript, and Vega Lite.}
            \resitem{Provided customers with real-time visibility into CPU, disk, and GPU usage through advanced monitoring components.}
        \end{itemize}
        \item \ressubheading{Snowflake}{Waterloo, Canada}{Software Engineer Intern}{Not Specified - Not Specified}
        \begin{itemize}
            \resitem{Designed and implemented an E2E testing framework adopted by 100+ engineers across 15+ teams using Jenkins, Docker, Groovy, Bash, and Datadog.}
            \resitem{Architected UI component APIs consumed by developers on 5+ teams using React.js and TypeScript.}
            \resitem{Deployed user experience enhancements across products used by 15,000+ users across 3,000+ organizations.}
        \end{itemize}
        \item \ressubheading{IBM}{Waterloo, Canada}{Software Developer Intern}{Not Specified - Not Specified}
        \begin{itemize}
            \resitem{Shipped a generative AI application for code explanation and test-case generation on 12M+ lines of code using AWS, React.js, and IBM's WatsonX AI platform.}
            \resitem{Increased code explanation accuracy from 30\% to 90\% by implementing Retrieval-Augmented Generation (RAG) using LangChain, FAISS vector database, Python, and the Mixtral 8x7B LLM.}
            \resitem{Engineered a rules-based anomaly detection system to verify \$10B+ in insurance claims using Python and SQL.}
        \end{itemize}
        \item \ressubheading{TD Bank}{Waterloo, Canada}{Software Developer Intern}{Not Specified - Not Specified}
        \begin{itemize}
            \resitem{Designed a distributed task queue to asynchronously execute portfolio model calculations using Celery and Python.}
            \resitem{Saved Portfolio Managers 10+ hours per week by eliminating wait times associated with synchronous executions.}
        \end{itemize}
        \item \ressubheading{University of Toronto}{Waterloo, Canada}{Research Intern}{Not Specified - Not Specified}
        \begin{itemize}
            \resitem{Contributed to a university-partnered study with OpenAI focusing on AI alignment in the workplace.}
            \resitem{Conducted research under the supervision of Dr. Meena Andiappan and Dr. Gillian Hadfield.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Projects}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Pethsapp}{}{Lead Developer}{Jun. 2021 - Jun. 2023}
        \begin{itemize}
            \resitem{Led a team of 5 in developing a mobile application for a high school community, serving 1200+ students, staff, and parents.}
            \resitem{Utilized React Native, Firebase, Google Cloud, and Sanity for full-stack development.}
            \resitem{Achieved Top 15 ranking on the Apple App Store Education Chart.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Education}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{University of Waterloo}{Waterloo, Canada}{Bachelor of Computer Science}{2022 - 2026}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Technical Skills}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] JavaScript, TypeScript, Python, SQL, C++, C, HTML, CSS, React.js, Next.js, Node.js, React Native, Celery, Django, Flask, Tailwind CSS, StyleX, PostgreSQL, SQL Server, MongoDB, Redis, Google Cloud, AWS, Snowflake, Vercel, Datadog, LangChain, FAISS, RAG, LLMs, Docker, Jenkins, gRPC, Protocol Buffers, Vega Lite
      \end{itemize}
    \end{document}