
    \documentclass[letterpaper,11pt]{article}
    \newlength{\outerbordwidth}
    \pagestyle{empty}
    \raggedbottom
    \raggedright
    \usepackage[svgnames]{xcolor}
    \usepackage{framed}
    \usepackage{tocloft}

    \usepackage[T1]{fontenc}
    \usepackage{lmodern}
    \usepackage[utf8]{inputenc}
    \usepackage[]{babel}
    \usepackage{fontawesome}
    \usepackage{hyperref}

    %-----------------------------------------------------------
    %Edit these values as you see fit

    \setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars
    \definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
    \definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

    %-----------------------------------------------------------
    %Margin setup

    \setlength{\evensidemargin}{-0.25in}
    \setlength{\headheight}{0in}
    \setlength{\headsep}{0in}
    \setlength{\oddsidemargin}{-0.25in}
    \setlength{\paperheight}{11in}
    \setlength{\paperwidth}{8.5in}
    \setlength{\tabcolsep}{0in}
    \setlength{\textheight}{9.5in}
    \setlength{\textwidth}{7in}
    \setlength{\topmargin}{-0.3in}
    \setlength{\topskip}{0in}
    \setlength{\voffset}{0.1in}

    %-----------------------------------------------------------
    %Custom commands
    \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
    \newcommand{\resheading}[1]{\vspace{6pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
    \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.8in][l]{\large #1} \vphantom{p\^{E}}}}}}
        \end{shaded}
    }\vspace{-6pt}
    }
    \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{p{4.8in}@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-8pt}}
    %-----------------------------------------------------------

    \begin{document}
    
      \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large Miguel Osuna} & +52 664 385 1469 \\
      Tijuana, B.C., Mexico & contact@miguel-osuna.com \\
      \faGithub { }  \href{https://github.com}{https://github.com} & \\
      \faLinkedin { }  \href{https://linkedin.com}{https://linkedin.com} & \\
      \faGlobe { }  \href{https://miguel-osuna.com}{https://miguel-osuna.com} & \\
      \end{tabular*}
      \vspace{5pt}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Summary}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
      \item[] Senior Software Engineer with over 5 years of expertise in developing scalable, high-availability applications and optimizing complex software ecosystems. Proven track record in driving operational efficiency through AI-driven enhancements, including a 25\% boost in quote conversions. Expert in full-stack development, cloud technologies (AWS, GCP), and modern CI/CD workflows using GitHub Actions. Highly skilled in streamlining developer productivity by optimizing CLI performance and automating package management. A dedicated collaborator experienced in working within large-scale monorepos and multi-brand platforms to deliver high-quality, production-ready software solutions.
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Work Experience}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{The Home Depot}{Tijuana, B.C., Mexico}{Senior Software Engineer}{Jul 2024 - Now}
        \begin{itemize}
            \resitem{Driving innovative solutions on the MyView team to enhance operational efficiency for thousands of store associates.}
            \resitem{Boosted quote conversion by approximately 25\% through the implementation of AI-driven enhancements.}
            \resitem{Developed a data-rich dashboard utilized by over 1,000 store associates for real-time operational insights.}
            \resitem{Upgraded 80+ test suites from Enzyme to React Testing Library, increasing code coverage by 20\% and reducing production bugs by ~15\%.}
        \end{itemize}
        \item \ressubheading{Expedia Group}{Tijuana, B.C., Mexico}{Senior Software Development Engineer}{Oct 2022 - May 2024}
        \begin{itemize}
            \resitem{Played a key role on the Bernie platform team, streamlining developer workflows and improving performance across multiple Expedia brands.}
            \resitem{Reduced CLI command execution time by ~50\% and cut overall build times by ~20\%.}
            \resitem{Migrated CI/CD pipelines to GitHub Actions, significantly streamlining release cycles and reducing deployment overhead.}
            \resitem{Automated package updates using Renovate, eliminating manual dependency management tasks.}
            \resitem{Implemented snapshot testing within the monorepo architecture, saving approximately 4 hours of manual effort weekly.}
        \end{itemize}
        \item \ressubheading{Expedia Group}{Tijuana, B.C., Mexico}{Software Development Engineer}{Mar 2021 - Oct 2022}
        \begin{itemize}
            \resitem{Contributed to Hotwire's Platform and the Cruise Customer Experience team, focusing on data-driven enhancements and reusable UI components.}
            \resitem{Optimized GraphQL queries, boosting data retrieval speed by ~20\% across key Cruise domain pages.}
            \resitem{Designed and implemented reusable UI components for Lodging, Flights, Packages, and Cruises to ensure design consistency.}
            \resitem{Reduced shared package bundle sizes to enhance frontend performance and loading speeds.}
            \resitem{Accelerated the migration of partner-facing applications, effectively halving developer onboarding time.}
        \end{itemize}
        \item \ressubheading{Prismview}{Tijuana, B.C., Mexico}{Software Engineer}{Aug 2015 - Jun 2020}
        \begin{itemize}
            \resitem{Developed and maintained high-availability software for large-format LED display systems.}
            \resitem{Maintained 99.9\% uptime for mission-critical LED display systems in commercial venues.}
            \resitem{Enhanced Banner CMS features, leading to a ~30\% reduction in customer-reported issues.}
            \resitem{Reduced the bug backlog by ~25\% through rigorous triaging and efficient debugging processes.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Education}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{Universidad Autónoma de Baja California}{Tijuana, B.C., Mexico}{B.S. Electronics Engineering}{Aug 2015 - Jun 2020}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Technical Skills}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] JavaScript, TypeScript, React.js, Node.js, Next.js, GraphQL, CSS, Java, Kotlin, Python, AWS, GCP, Docker, GitHub Actions, CI/CD, AI-driven Enhancements, Monorepo Management, Unit/Snapshot Testing, API Optimization
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Languages}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] \textbf{English}: Native
		    \item[] \textbf{Spanish}: Native
      \end{itemize}
    \end{document}