
    \documentclass[letterpaper,11pt]{article}
    \newlength{\outerbordwidth}
    \pagestyle{empty}
    \raggedbottom
    \raggedright
    \usepackage[svgnames]{xcolor}
    \usepackage{framed}
    \usepackage{tocloft}

    \usepackage[T1]{fontenc}
    \usepackage{lmodern}
    \usepackage[utf8]{inputenc}
    \usepackage[]{babel}
    \usepackage{fontawesome}
    \usepackage{hyperref}

    %-----------------------------------------------------------
    %Edit these values as you see fit

    \setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars
    \definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
    \definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

    %-----------------------------------------------------------
    %Margin setup

    \setlength{\evensidemargin}{-0.25in}
    \setlength{\headheight}{0in}
    \setlength{\headsep}{0in}
    \setlength{\oddsidemargin}{-0.25in}
    \setlength{\paperheight}{11in}
    \setlength{\paperwidth}{8.5in}
    \setlength{\tabcolsep}{0in}
    \setlength{\textheight}{9.5in}
    \setlength{\textwidth}{7in}
    \setlength{\topmargin}{-0.3in}
    \setlength{\topskip}{0in}
    \setlength{\voffset}{0.1in}

    %-----------------------------------------------------------
    %Custom commands
    \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
    \newcommand{\resheading}[1]{\vspace{6pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
    \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.8in][l]{\large #1} \vphantom{p\^{E}}}}}}
        \end{shaded}
    }\vspace{-6pt}
    }
    \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{p{4.8in}@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-8pt}}
    %-----------------------------------------------------------

    \begin{document}
    
      \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large Caitlin Chiang} & 8451-0986 \\
      Singapore, Singapore & chiangcaitlin2003@gmail.com \\
      \faGlobe { }  \href{https://caitlinchiang.xyz/}{https://caitlinchiang.xyz/} & \\
      \faLinkedin { }  \href{linkedin.com/in/caitlin-chiang}{linkedin.com/in/caitlin-chiang} & \\
      \end{tabular*}
      \vspace{5pt}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Summary}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
      \item[] Highly accomplished Software Engineer specializing in Artificial Intelligence and full-stack development, with a proven track record of taking complex AI-centric applications from ideation to production. Expertise spans building multi-agent AI platforms, architecting scalable fintech infrastructure, and leading cross-functional teams in high-stakes environments including Y-Combinator startups and major academic-industry partnerships. Proficient in designing event-driven architectures, integrating LLM providers, and developing responsive, data-driven interfaces. Demonstrated ability to bridge the gap between technical implementation and stakeholder requirements, making her uniquely qualified to translate cutting-edge AI into impactful real-world solutions.
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Work Experience}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Xweave.io}{Singapore, Singapore}{Software Engineer}{May 2025 - Now}
        \begin{itemize}
            \resitem{Architected and delivered secure integrations with multiple digital asset exchange providers using standardized REST APIs for scalable cross-border payment orchestration.}
            \resitem{Designed and productionized an event-driven webhook architecture to ensure reliable, real-time transaction synchronization across distributed systems.}
            \resitem{Implemented a modular mid-market rate service using object-oriented design principles for efficient retrieval and synchronization of fiat and cryptocurrency exchange rates.}
            \resitem{Led and mentored two software engineers through technical guidance, code reviews, and architectural discussions to improve engineering quality and delivery velocity.}
        \end{itemize}
        \item \ressubheading{Liminal}{Singapore, Singapore}{AI Software Engineer}{Not specified - Not specified}
        \begin{itemize}
            \resitem{Engineered a production-ready full-stack multi-agent AI platform featuring configurable workflows, dynamic query execution, and customizable result management.}
            \resitem{Developed a responsive React-based chat interface incorporating editable tables, configurable schemas, and real-time data visualization.}
            \resitem{Architected a modular backend platform integrating multiple LLM providers and advanced prompt engineering strategies for scalable feature development.}
        \end{itemize}
        \item \ressubheading{Moya}{Singapore, Singapore}{Software Engineer}{Oct 2024 - Mar 2025}
        \begin{itemize}
            \resitem{Engineered automated data processing pipelines to aggregate, transform, and consolidate large-scale CSV datasets into standardized analytical outputs.}
            \resitem{Designed reusable scripts to generate abatement curves and analytical datasets, significantly improving data processing efficiency and consistency.}
        \end{itemize}
        \item \ressubheading{Jublia}{Singapore, Singapore}{Software Engineer}{Aug 2023 - Dec 2023}
        \begin{itemize}
            \resitem{Modernized a legacy Vue.js application by refactoring components into a modular, maintainable architecture to improve scalability.}
            \resitem{Redesigned a user-centric dashboard experience, enhancing usability and application navigation.}
            \resitem{Automated database integrity validation through scheduled monitoring scripts, reducing manual verification efforts and improving operational reliability.}
        \end{itemize}
        \item \ressubheading{SUTD campusX}{Singapore, Singapore}{Software Engineer}{Jan 2023 - Dec 2023}
        \begin{itemize}
            \resitem{Collaborated with faculty and stakeholders to architect and deliver an AI-powered learning platform focused on enhancing educational workflows.}
            \resitem{Engineered a modular application framework highly configurable for various university course requirements.}
            \resitem{Defined system architecture and relational database design with an emphasis on scalability, maintainability, and long-term extensibility.}
        \end{itemize}
        \item \ressubheading{Dashlabs.ai}{Singapore, Singapore}{Software Engineer}{Dec 2020 - Dec 2021}
        \begin{itemize}
            \resitem{Led and mentored a team of seven software engineers in building healthcare analytics solutions for a Y-Combinator backed healthtech startup.}
            \resitem{Translated complex clinical requirements from medical professionals into scalable, production-ready analytical software.}
            \resitem{Delivered over 30 production features that streamlined healthcare workflows and improved operational efficiency.}
            \resitem{Engineered over 20 interactive analytics dashboards and architected data aggregation pipelines to transform complex healthcare datasets into actionable visual insights.}
        \end{itemize}
        \item \ressubheading{Philippine Red Cross}{Singapore, Singapore}{Software Engineer}{Jul 2021 - Oct 2021}
        \begin{itemize}
            \resitem{Developed automated module-level testing scripts to improve software reliability, maintainability, and deployment confidence.}
        \end{itemize}
        \item \ressubheading{Dragonpay Corporation}{Singapore, Singapore}{Freelance Software Engineer}{Jun 2021 - Jul 2021}
        \begin{itemize}
            \resitem{Developed and deployed an internal employee wellness platform for organizational health tracking.}
            \resitem{Engineered an internal expense management application to automate financial workflows for the finance team.}
        \end{itemize}
        \item \ressubheading{Various Clients (The Rolls Kitchen, The Busy Bee, Soren Apparel)}{Singapore, Singapore}{Freelance Software Engineer}{Mar 2020 - Jun 2021}
        \begin{itemize}
            \resitem{Partnered with business owners to translate business objectives into scalable web application solutions.}
            \resitem{Designed and developed end-to-end e-commerce platforms including customer-facing sites and administrative management systems.}
            \resitem{Architected application databases and backend systems optimized for maintainability and long-term growth.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Projects}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Urban Redevelopment Authority (URA) AI Platform}{}{Team Lead and Software Engineer}{Jan 2024 - May 2024}
        \begin{itemize}
            \resitem{Led a team of four engineers to deliver an AI-powered public engagement platform that transforms user ideas into AI-generated visual concepts.}
            \resitem{Integrated advanced generative AI techniques, including prompt engineering and image inpainting, to enhance image quality and user experience.}
            \resitem{Designed a modular application architecture allowing administrators to customize engagement workflows without code changes.}
            \resitem{Successfully translated UX designs into production-ready software with high fidelity to design specifications.}
        \end{itemize}
        \item \ressubheading{Development Bank of Singapore (DBS) Queue Simulation}{}{Team Lead and Software Engineer}{May 2023 - Aug 2023}
        \begin{itemize}
            \resitem{Led a team of five engineers to develop a configurable web-based queue simulation platform for banking branch operational planning.}
            \resitem{Architected a scalable and modular system design to support flexible simulation scenarios and future platform extensibility.}
        \end{itemize}
        \item \ressubheading{Procter \& Gamble (P\&G) Consumer Analytics Platform}{}{Technical Lead and Software Engineer}{Sept 2024 - Dec 2024}
        \begin{itemize}
            \resitem{Led a team of six engineers to deliver a data visualization platform for P\&G's R\&D organization to analyze consumer behavior.}
            \resitem{Engineered automated CSV ingestion and processing pipelines to transform raw datasets into interactive analytical visualizations.}
            \resitem{Developed interactive dashboards enabling multi-dimensional data comparison via configurable timelines and visual analytics.}
            \resitem{Integrated AI-powered image analysis techniques to extract visual attributes and emotional signals from consumer-submitted images for research insights.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Education}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{Singapore University of Technology and Design (SUTD)}{Singapore, Singapore}{Bachelor of Science in Design and Artificial Intelligence}{Sept 2021 - May 2025}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Technical Skills}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] JavaScript, TypeScript, Python, Ruby, HTML, CSS, React.js, Next.js, Vue.js, Material UI, Chakra UI, Node.js, Express.js, Flask, Ruby on Rails, LangChain, LangGraph, PostgreSQL, MySQL, MongoDB, Firebase, REST APIs, GraphQL (Apollo), Amazon Web Services (AWS), Google Cloud Platform (GCP), Cloudinary, Netlify, Git, Cypress, Snakemake, Generative AI, Prompt Engineering, Multi-agent AI Systems, Full-stack Development, UX/UI Design
      \end{itemize}
    \end{document}