
    \documentclass[letterpaper,11pt]{article}
    \newlength{\outerbordwidth}
    \pagestyle{empty}
    \raggedbottom
    \raggedright
    \usepackage[svgnames]{xcolor}
    \usepackage{framed}
    \usepackage{tocloft}

    \usepackage[T1]{fontenc}
    \usepackage{lmodern}
    \usepackage[utf8]{inputenc}
    \usepackage[]{babel}
    \usepackage{fontawesome}
    \usepackage{hyperref}

    %-----------------------------------------------------------
    %Edit these values as you see fit

    \setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars
    \definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
    \definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

    %-----------------------------------------------------------
    %Margin setup

    \setlength{\evensidemargin}{-0.25in}
    \setlength{\headheight}{0in}
    \setlength{\headsep}{0in}
    \setlength{\oddsidemargin}{-0.25in}
    \setlength{\paperheight}{11in}
    \setlength{\paperwidth}{8.5in}
    \setlength{\tabcolsep}{0in}
    \setlength{\textheight}{9.5in}
    \setlength{\textwidth}{7in}
    \setlength{\topmargin}{-0.3in}
    \setlength{\topskip}{0in}
    \setlength{\voffset}{0.1in}

    %-----------------------------------------------------------
    %Custom commands
    \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
    \newcommand{\resheading}[1]{\vspace{6pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
    \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.8in][l]{\large #1} \vphantom{p\^{E}}}}}}
        \end{shaded}
    }\vspace{-6pt}
    }
    \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{p{4.8in}@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-8pt}}
    %-----------------------------------------------------------

    \begin{document}
    
      \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large SAMI ALHARBI} & +966 53 113 1327 \\
      Riyadh, Saudi Arabia & sami.obeid@outlook.com \\
      \faGlobe { }  \href{Portfolio}{Portfolio} & \\
      \faGlobe { }  \href{LinkedIn}{LinkedIn} & \\
      \faGlobe { }  \href{GitHub}{GitHub} & \\
      \end{tabular*}
      \vspace{5pt}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Summary}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
      \item[] Results-driven Software Engineer with nearly 3 years of experience specializing in full-stack development, microservices architecture, and cloud-native technologies. Proven expertise in building scalable web applications and integrating advanced technologies such as Tesseract OCR and Elasticsearch for enhanced search and data extraction capabilities. Proficient in modern software development practices including CI/CD, Docker containerization, and event-driven architectures using Kafka. A continuous learner with a strong foundation in Java, .NET, and JavaScript, dedicated to delivering high-quality, impactful software solutions through Agile methodologies.
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Work Experience}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Confidential Government Agency}{Riyadh, Saudi Arabia}{Software Engineer}{Dec 2024 - Now}
        \begin{itemize}
            \resitem{Designed and architected a comprehensive document upload feature, facilitating seamless end-user interaction and system integration.}
            \resitem{Integrated Tesseract OCR for automated text extraction and implemented Elasticsearch with an Arabic analyzer to enable high-quality full-text semantic search.}
            \resitem{Engineered an automated retry mechanism using Cronjobs to ensure reliable and resilient OCR processing.}
            \resitem{Applied the Saga pattern to maintain strict data consistency across a distributed architecture involving MongoDB, MinIO, and Elasticsearch.}
            \resitem{Developed a scalable audit logging system to track system-wide changes, capturing before/after state values, user identification, and precise timestamps.}
            \resitem{Leveraged event-driven architecture with Kafka to facilitate non-blocking, asynchronous communication, significantly improving system performance and scalability.}
            \resitem{Managed deployment of containerized applications using Docker and optimized traffic management via Nginx reverse proxy.}
        \end{itemize}
        \item \ressubheading{Wakeb}{Riyadh, Saudi Arabia}{Software Engineer}{Mar 2023 - Dec 2024}
        \begin{itemize}
            \resitem{Developed and maintained robust RESTful APIs to support core business logic and system interoperability.}
            \resitem{Implemented complex integrations using UDP, API, and MQTT protocols to enable real-time data synchronization across disparate systems.}
            \resitem{Conducted extensive field testing to validate system reliability and performance in real-world environments.}
            \resitem{Established rigorous code review processes and Git branching strategies to enhance code quality and streamline collaborative development.}
            \resitem{Mentored junior developers on industry best practices and facilitated the adoption of modern technological stacks.}
            \resitem{Actively participated in Agile ceremonies, including sprint planning and retrospectives, to drive continuous improvement in delivery cycles.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Projects}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Riyadh Real Estate Bot}{}{Developer}{Now}
        \begin{itemize}
            \resitem{Developed an autonomous multi-platform social media bot designed to track and share Riyadh real estate deals in real time.}
        \end{itemize}
        \item \ressubheading{CarShowroom Management System}{}{Developer}{Now}
        \begin{itemize}
            \resitem{Developed a full-stack application featuring complete CRUD operations, data validation, pagination, and HATEOAS implementation.}
            \resitem{Engineered a complete CI/CD pipeline with automated deployment across development, staging, and production environments using Docker containers and a private registry.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Education}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{Qassim University}{Riyadh, Saudi Arabia}{Information Technology}{2018 - 2023}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Courses \& Certifications}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{Java Web Developer Nanodegree}{Udacity}{}{Now}
		    \item \ressubheading{Certified Kubernetes Application Developer (CKAD)}{Cloud Native Computing Foundation}{}{Now}
		    \item \ressubheading{Angular - The Complete Guide (2024 Edition)}{Udemy}{}{Now}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Technical Skills}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] C\#, Java, JavaScript, ASP.NET Core, .NET, Spring Boot, Node.js, Express, React, Vue.js, Next.js, Angular, RESTful APIs, gRPC, MQTT, UDP, Elasticsearch, MongoDB, PostgreSQL, Redis, MinIO, Kafka, Docker, Kubernetes, Nginx, CI/CD, Jenkins, Git, Agile/Scrum, Microservices, Saga pattern, Tesseract OCR, Semantic Search
      \end{itemize}
    \end{document}