
    \documentclass[letterpaper,11pt]{article}
    \newlength{\outerbordwidth}
    \pagestyle{empty}
    \raggedbottom
    \raggedright
    \usepackage[svgnames]{xcolor}
    \usepackage{framed}
    \usepackage{tocloft}

    \usepackage[T1]{fontenc}
    \usepackage{lmodern}
    \usepackage[utf8]{inputenc}
    \usepackage[]{babel}
    \usepackage{fontawesome}
    \usepackage{hyperref}

    %-----------------------------------------------------------
    %Edit these values as you see fit

    \setlength{\outerbordwidth}{2pt}  % Width of border outside of title bars
    \definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
    \definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

    %-----------------------------------------------------------
    %Margin setup

    \setlength{\evensidemargin}{-0.25in}
    \setlength{\headheight}{0in}
    \setlength{\headsep}{0in}
    \setlength{\oddsidemargin}{-0.25in}
    \setlength{\paperheight}{11in}
    \setlength{\paperwidth}{8.5in}
    \setlength{\tabcolsep}{0in}
    \setlength{\textheight}{9.5in}
    \setlength{\textwidth}{7in}
    \setlength{\topmargin}{-0.3in}
    \setlength{\topskip}{0in}
    \setlength{\voffset}{0.1in}

    %-----------------------------------------------------------
    %Custom commands
    \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
    \newcommand{\resheading}[1]{\vspace{6pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
    \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{2pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.8in][l]{\large #1} \vphantom{p\^{E}}}}}}
        \end{shaded}
    }\vspace{-6pt}
    }
    \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{p{4.8in}@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-8pt}}
    %-----------------------------------------------------------

    \begin{document}
    
      \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\Large Yi Zhen} & +86 177 1768 7328 \\
      Shanghai, China & iamzhenyi@gmail.com \\
      \faGithub { }  \href{https://github.com/i-zhen}{https://github.com/i-zhen} & \\
      \faLinkedin { }  \href{https://linkedin.com/in/izhenyi}{https://linkedin.com/in/izhenyi} & \\
      \faGlobe { }  \href{https://izhen.me}{https://izhen.me} & \\
      \end{tabular*}
      \vspace{5pt}

      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Summary}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
      \item[] Senior Software Engineer and Tech Architect with extensive expertise in AI systems, LLM optimization, and high-performance compiler frameworks. Proven track record in leading technical teams to build large-scale, production-ready AI infrastructure, including LLM deployment, model compression, and operator development. Experienced in managing the full lifecycle of complex technical projects, from research-driven ideation to the implementation of open-source frameworks and university-enterprise collaborations. Expert in bridging the gap between cutting-edge AI research and robust software engineering, specializing in high-performance computing, smart contract compilers, and domain-specific languages.
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Work Experience}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{Ant Group}{Shanghai, China}{Senior Software Engineer, Team Lead \& Tech Architect}{Mar. 2021 - Now}
        \begin{itemize}
            \resitem{Architecting and building advanced AI systems focused on the optimization of LLM performance and operator development.}
            \resitem{Leading a specialized engineering team to develop 'SIR', a pioneering open-source smart contract compiler framework on AntChainOpenLabs.}
            \resitem{Managing the end-to-end development of the Gödel query language, a high-performance DSL for data processing.}
            \resitem{Driving innovation through strategic university-enterprise cooperation projects with Sun Yat-sen University (SYSU).}
        \end{itemize}
        \item \ressubheading{Huawei Research}{Shanghai, China}{Software Engineer, Tech Lead, Development}{Nov. 2018 - Mar. 2021}
        \begin{itemize}
            \resitem{Served as Tech Lead for the design and implementation of a high-impact low-code development platform.}
            \resitem{Acted as a core developer for the Open Ark compiler, contributing to advanced compilation technology.}
        \end{itemize}
        \item \ressubheading{Citigroup}{Shanghai, China}{Software Engineer, Development, Continuous Integration}{Apr. 2017 - Nov. 2018}
        \begin{itemize}
            \resitem{Engineered critical components for an anti-money laundering (AML) platform.}
            \resitem{Developed and maintained the wire transfer system for block trade agents, ensuring high reliability and compliance.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \resheading{Projects}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
        \item \ressubheading{LLM Optimization of Training and Inference}{}{Tech Lead}{Feb. 2024}
        \begin{itemize}
            \resitem{Driving LLM deployment and training strategies to maximize computational efficiency.}
            \resitem{Implementing model compression techniques and performing rigorous LLM performance profiling.}
            \resitem{Developing and tuning specialized operator libraries for high-performance LLM inference and evaluation.}
        \end{itemize}
        \item \ressubheading{Smart Intermediate Representation (SIR)}{}{Smart Contract Compiler Framework Co-founder}{Nov. 2022 - Jan. 2024}
        \begin{itemize}
            \resitem{Co-founded a universal technical solution designed to enhance safety and performance for smart contracts across various programming languages.}
            \resitem{Developed a framework to ensure multi-scenario compatibility for blockchain platforms.}
        \end{itemize}
        \item \ressubheading{Gödel Query Language}{}{Project Manager}{Jul. 2021 - Oct. 2022}
        \begin{itemize}
            \resitem{Developed a high-performance query language and compiler powered by a Datalog engine.}
            \resitem{Designed a Rust-like DSL for CodeFuse-Query, featuring strict type checking, type inference, and advanced error messaging.}
        \end{itemize}
        \item \ressubheading{ERC721G: Anti-Theft ERC721 Solution}{}{Co-founder}{Jun. 2022 - Oct. 2022}
        \begin{itemize}
            \resitem{Developed the world's first anti-theft NFT series solution, providing a universal technical layer to protect ERC721 smart contract assets.}
        \end{itemize}
        \item \ressubheading{PPrinter: A generic derivable Haskell pretty printer}{}{Author}{Jun. 2016 - Aug. 2016}
        \begin{itemize}
            \resitem{Created a Haskell library enabling automatic derivation of pretty-printing functions for arbitrary user-defined data types.}
        \end{itemize}
        \item \ressubheading{Sun Yat-sen University ASC Student Supercomputer Challenge Team}{}{Team member}{2014 - 2014}
        \begin{itemize}
            \resitem{Mastered numerical methods, GPGPU heterogeneous computing, and multiprocessor programming.}
            \resitem{Optimized the SU 2 (Stanford University open-source C++ code for PDE analysis) and assisted in HPL performance benchmarks.}
        \end{itemize}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Education}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item \ressubheading{University of Edinburgh}{Shanghai, China}{Artificial Intelligence}{Sep. 2015 - Nov. 2016}
		    \item \ressubheading{Sun Yat-sen University}{Shanghai, China}{Software Engineering}{Sep. 2011 - Jun. 2015}
      \end{itemize}
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \resheading{Technical Skills}
	    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	    \begin{itemize}
		    \item[] LLM Optimization, LLM Deployment, Model Compression, Performance Profiling, AI Systems Architecture, Operator Development, Smart Contract Compiler Frameworks, Datalog, Rust, Python, C++, Haskell, C, CUDA, Triton, MLIR, LLVM, vLLM, SGLang, ONNXRuntime, Solidity, TypeScript, Scala, Java, Prolog, Coq, ASM, web3.js, ether.js, Hardhat, Tilelang, Project Management, Continuous Integration (CI/CD)
      \end{itemize}
    \end{document}